Statistics Project

### 2022-12-10 rough_analysis.Rmd
small typos, needs relook
Rough Completion of FS/ BE/ SW model generation

SalePrice ~ SqFt (GrLIvArea)

@@

```{r echo=FALSE}
library(tidyverse)
library(plotly)

housing = read.csv(file = "train.csv")
a1_set = housing %>% select(SalePrice, Neighborhood, GrLivArea) %>% filter( Neighborhood == c("NAmes", "Edwards", "BrkSide"))
```

@@

```{r}
#drive home a comparision in means to signify a difference in mean values.
n_means <- aov(SalePrice ~ Neighborhood, data = a1_set)
mean_diff <- TukeyHSD(n_means, conf.level = 0.95)
mean_diff
fit <- lm(SalePrice ~ GrLivArea + Neighborhood + GrLivArea*Neighborhood, data = a1_set)
```

>>>>

SalePrice ~ SqFt (GrLIvArea) + Neighborhood

@@

```{r echo=FALSE}
library(tidyverse)
library(plotly)
library(car)

housing = read.csv(file = "train.csv")
numeric_housing = housing %>% select_if(is.numeric)
a1_set = housing %>% select(SalePrice, Neighborhood, GrLivArea) %>% filter( Neighborhood == c("NAmes", "Edwards", "BrkSide"))
```

@@

```{r}
#Comparison of Means/Coefficients to signify a difference in sample groups from different neighborhoods.
n_means <- aov(SalePrice ~ Neighborhood, data = a1_set)
mean_diff <- TukeyHSD(n_means, conf.level = 0.95)
mean_diff
fit <- lm(SalePrice ~ GrLivArea + Neighborhood + GrLivArea*Neighborhood, data = a1_set)
```

Analysis 2:

Rough approach to Forwards Selection / Backwards Elimination / Stepwise Selection model generation:

library(caret)
train.control = trainControl(method = "cv", number = 10)
step.model = train(SalePrice ~.-GarageArea, data = housing %>% select_if(is.numeric) %>% drop_na(), method = "leapBackward", trControl = train.control)
step.model$modelInfo
```

For the process of forward feature selection or backwards feature elimination, we can use the olsrr package to do most of the calculations for us. This can be seen as follows:

```{r}
#install.packages("olsrr")
library(olsrr)

#turning all character columns into factors for LR: 
character_names = housing %>% select_if(is.character) %>% names()
housing[character_names] = lapply(housing[character_names], factor)

fit_numeric = lm(SalePrice ~., data = housing %>% select_if(is.numeric))

#forwards selection: 
forward = ols_step_forward_p(fit_numeric, penter = 0.05, details = FALSE)

backwards = ols_step_backward_p(fit_numeric, prem = 0.05, details = FALSE)

stepwise = ols_step_both_p(fit_numeric, pent = 0.05, prem =0.05, details = FALSE)
```

```{r}
for(i in housing %>% names()){
  print(nlevels(housing %>% select(i)))
}

lapply(housing[character_names], nlevels)
```
